### 2014-11-13 tex/related.tex
updates to related work

Recent years have seen a significant growth in research projects based
on symbolic execution, first introduced in the 1970's by
Clarke~\cite{Clarke:76} and King~\cite{King:76}.  These projects have
pursued three primary research directions to enhance traditional
symbolic execution: (1)~to improve its
effectiveness~\cite{Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit,Pasareanu:2011};
(2)~to improve its
efficiency~\cite{AnandETAL2009AbsSymExe,KhurshidSuen2005AbsSymExe,Godefroid:POPL07,Inkumsah:2008,ChangPhD10DataFlowSymbolicExecution,Santelices:ISSTA10,Visser:2012};
and (3)~to improve its
applicability~\cite{Person:FSE08,KhurshidETAL05RepairingStructurally,CsallnerETAL08DySy,SeoETAL06EnergyConsumptionFrameworkDistributedJava,Geldenhuys:2012,Ma:2011}. Handling
unbounded data input of complex type has continued to be a challenge
for symbolic execution.  Generalized symbolic execution \cite{GSE03}
with lazy initialization set the path to materializing fields
concretely. Subsequent improvements to the method
\cite{Deng:2006,Deng:2007} to reduce path explosion by delaying path
splitting over aliasing choices for as long as possible. However,
since all of the above methods introduce nondeterminism during field
reads and writes, they all contribute to path explosion to some
extent.

@@

A number of static analysis techniques have been proposed that have
some ability to reason about input heap structures. One notable static
analysis method that is closely related to ours is the procedure
summaries proposed by Isil and Tomas Dillig \cite{Dillig:2011}.  While
their method has improved path sensitivity over standard static
analysis methods, it remains limited by a statically-generated
symbolic input heap, and cannot adapt to path-sensitive heap
properties of the input heap.

@@

As in our representation, other methods have been proposed that model
references using sets of guarded locations
\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These sets,
sometimes known as value sets or value summaries, allow multiple heaps
to be represented simultaneously with a higher degree of precision
than afforded by shape analysis. However, some of these previous
attempts \cite{Xie:2005,Cherem:2007} utilize non-local recursive
definitions for objects. The impact of using recursive definitions for
objects is two-fold. First, these techniques must use approximations
to resolve reference inequalities, resulting in false positives in the
results. Second, these techniques are incapable of reasoning about
heaps with recursive data structures due to the potential for infinite
recursion during dereferencing. This means that either a large class
of data structures must be avoided, or a large class of behaviors must
be ignored. In our heap representation, object descriptions are
entirely local, thus avoiding these pitfalls. Other methods
\cite{Dillig:2011,Sen:2014}, while having local morphological
representations, do not provide for dynamic exploration of the initial
heap state.

Another line of work in heap representation lies in identifying
isomorphic heap structures in order to avoid exploring redundant
paths. Examples of such methods include Korat, XXX, and YYY. These
methods are generally focused on the morphology of the heap alone, in
isolation from the external constraint problems encountered during
program execution. As such, these works are largely orthogonal to the
methods presented here, though some of them may possibly be
complimentary.

>>>>

Recent years have seen a significant growth in research projects based
on symbolic execution, first introduced in the 1970's by
Clarke~\cite{Clarke:76} and King~\cite{King:76}. Initial work on symbolic
execution largely focused on checking properties of program with
primitive types. Several recent projects generalized the core
idea of symbolic execution which enabled it to be applied to
programs with more general types, including references and 
arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during symbolic
execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths
than GSE techniques.

%These projects have
%pursued three primary research directions to enhance traditional
%symbolic execution: (1)~to improve its
%effectiveness~\cite{Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit,Pasareanu:2011};
%(2)~to improve its
%efficiency~\cite{AnandETAL2009AbsSymExe,KhurshidSuen2005AbsSymExe,Godefroid:POPL07,Inkumsah:2008,ChangPhD10DataFlowSymbolicExecution,Santelices:ISSTA10,Visser:2012};
%and (3)~to improve its
%applicability~\cite{Person:FSE08,KhurshidETAL05RepairingStructurally,CsallnerETAL08DySy,SeoETAL06EnergyConsumptionFrameworkDistributedJava,Geldenhuys:2012,Ma:2011}.
%analyzing programs containing complex data structure with unbounded
%domains continues to be challenging
%for symbolic execution techniques.  Generalized symbolic execution \cite{GSE03}
%with lazy initialization set the path to materializing fields
%concretely. Subsequent improvements to the method
%\cite{Deng:2006,Deng:2007} to reduce path explosion by delaying path
%splitting over aliasing choices for as long as possible. However,
%since all of the above methods introduce nondeterminism during field
%reads and writes, they all contribute to path explosion to some
%extent.

@@

A number of static analysis techniques have been proposed
to support reasoning about input heap structures~\cite{}. The technique
most closely related to (and which served as inspiration for) our approach
is the procedure summary proposed by Dillig et al. to support modular
reasoning~\cite{Dillig:2011}.  While
their method improves path sensitivity over standard static
analysis methods, it remains limited by a statically-generated
symbolic input heap and it cannot adapt to path-sensitive heap
properties of the input heap.

@@

Other techniques have been proposed to model
references using sets of guarded
locations~\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These sets,
sometimes known as value sets or value summaries, allow multiple heaps
to be represented simultaneously with a higher degree of precision
than afforded by shape analysis. However, some of these previous
attempts~\cite{Xie:2005,Cherem:2007} utilize non-local recursive
definitions for objects. The impact of such an approach is two-fold. 
First, these techniques must use approximations
to resolve reference inequalities, resulting in false positives in the
results. Second, these techniques are incapable of reasoning about
heaps with recursive data structures due to the potential for infinite
recursion during dereferencing. This means that either a large class
of data structures must be avoided, or a large class of behaviors must
be ignored. In our heap representation, object descriptions are
entirely local, thus avoiding these pitfalls. Other methods
\cite{Dillig:2011,Sen:2014}, while having local morphological
representations, do not provide for dynamic exploration of the initial
heap state.

Another line of work in heap representation lies in identifying
isomorphic heap structures in order to avoid exploring redundant
paths. Examples of such methods include Korat~\cite{Milicevic:2007},
XXX, and YYY. These
methods are generally focused on the morphology of the heap apart
from the external constraint problems encountered during
program execution, and as such, are largely orthogonal to this work.
